### 2017-04-01 paper/evaluation.tex
fixing organization of section 3
fixing methodology and macros on RQX

@@

According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelization setting depends either on (1) \CodeIn{parallel} to
define the parallelism level within a JVM followed by
\CodeIn{threadCounter} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
in older versions) to define the number of forked JVMs. For each test
execution, we look for theses parameters and their values to classify
them.  \Jbc{Missing: explain how we mapped the configurations to
parallel level.} Figure~\ref{fig:freqmodes-dynamic} summarizes our
findings.

@@

To extend our initial investigation, we mined several \pomf{} files
from all \numMedLong{} projects classified as the \medg{} and
\longg{}-running.
\Jbc{rework this... $\rightarrow$}To reduce the number of build files
to inspect, we consider only must contain one of these keywords that
contain parallelization keywords, namely \CodeIn{forkMode},
\CodeIn{forkCount}, and \CodeIn{parallel}.  This mining step, however,
is not sound as a matching project may not indicate a project with a
valid configuration for running tests in parallel.  False positive can
happen because of comments, for instance.  To eliminate the cases of
false positives and also to categorize true positive cases, we
complemented the initial mining step with a manual inspection of
files.

%% settings); the second step (inspection) consists in a manual
%% inspection to confirm the presence of parallelism settings in the
%% build file and classify them according to the parallelism level.
%% Figure \Fix{removed} describes the discovery step: we list the paths
%% of all build files and filter only the files that contain any of the

@@

From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
where \numPomMatched{} of those files match one of the keywords
mentioned above.  From these \numPomMatched{} build files, we
eliminated six false-positives: two were names of project modules
(\eg, \emph{camel-cookbook-parallel-processing}), one was part of a
comment, and three were commented configurations. The
\numPomMatchedValid{} build files with valid configurations are
distributed across \numProjectsPar{} projects from our sample.
% 
% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}

\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group} %1st row, 1st cell
            & \multirow{2}{*}{\# \pomf{}}
            & \# \pomf{} matched
            & \# projects matched\\%
        % 2nd row - empty cell
            & % empty cell
            & (false-positives)
            & / total\\%
        \midrule%
        Long   & 1613 & 79 (1) & 19 / \numLong{}\\%
        Medium & 1238 & 30 (5) & 22 / \numMed{}\\%
        \midrule%
        Total % last row, first cell
            & \pomMedLong{}
            & \numPomMatched{} (6)
            & \numProjectsPar{} / \numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallelization settings in build files: the
    first column indicates the group of projects according to their
    time cost; the second column indicates the number of build files;
    the third column is the subset of files with parallelization
    keywords; the last column indicates the ratio of projects with
    parallelism support.}
    \label{tab:inspection-table} 
\end{figure}

\Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
identified above, we investigated further the \numPomMatchedValid{}
build files with parallel settings.  We analyzed the support and
distribution of parallel modes from this subset of projects. To
calculate the distribution of parallel modes, we considered only the
presence of the mode in at least one of the project settings.  Recall
that a build file may contain more than one parallel setting and a
project may contain several sub-modules with build files.  In case the
value of a parallel option is resolved dynamically (\eg, via
command-line argument or system variable) we compute all modes related
to the option. For instance, depending on the value, the
\CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes-static} summarizes our findings.
\Fix{Missing conclusion: Fork the most used configuration}

@@

To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
analyzed the \numProjectsPar{} subjects looking for the parallelism 
configuration inside the \pomf{} of each module. To run the subjects
sequentially, we manually modified the Maven Surefire configuration
from the \numPomMatchedValid{} identified before to not run in parallel.
The Figure~\ref{fig:surefire-configuration} show the injected configuration
in each \pomf{}.

>>>>

To enforce sequential execution, \Luis{rework this $\rightarrow$} we 
analyzed the \numProjectsPar{} subjects looking for the parallelism 
configuration inside the \pomf{} of each module. To run the subjects
sequentially, we manually modified the Maven Surefire configuration
from the \numPomMatched{} identified before to not run in parallel.
The Figure~\ref{fig:surefire-configuration} show the injected configuration
in each \pomf{}.

@@

According to Maven's documentation~\cite{maven-surefire-plugin}, any
parallelization setting depends either on (1) \CodeIn{parallel} to
define the parallelism level within a JVM followed by
\CodeIn{threadCount} or (2) \CodeIn{forkCount} (or \CodeIn{forkMode}
in older versions) to define the number of forked JVMs. For each test
execution, we look for theses parameters and their values to classify
them.  \Jbc{Missing: explain how we mapped the configurations to
parallel level.} Figure~\ref{fig:freqmodes-dynamic} summarizes our
findings.

@@

To extend our initial investigation, we mined several \pomf{} files
from all \numMedLong{} projects classified as the \medg{} and
\longg{}-running.
\Luis{rework this... $\rightarrow$}To reduce the number of build files
to inspect, we consider only \pomf{} files that contain the
configuration node inside a \CodeIn{plugin} tag with a child tag named
\CodeIn{artifactId} with the content \CodeIn{maven-surefire-plugin}.
This mining step, however, is not sound as a matching project may not 
indicate a project with a valid configuration for running tests in parallel.
\Comment{
False positive can happen because of comments, for instance.  
To eliminate the cases of false positives and also to categorize 
true positive cases, we complemented the initial mining step with a 
manual inspection of files.
}
%% settings); the second step (inspection) consists in a manual
%% inspection to confirm the presence of parallelism settings in the
%% build file and classify them according to the parallelism level.
%% Figure \Fix{removed} describes the discovery step: we list the paths
%% of all build files and filter only the files that contain any of the

@@

From the \numMedLong{} subjects, we found \pomMedLong{} \pomf{} files
where \numPomMatched{} of those files match one of the keywords
mentioned above.  From these \numPomMatched{} build filesi. The
\numPomMatched{} configurations are distributed across \numProjectsPar{} 
projects from our sample.
% 
% \emph{From these results we found that $\sim$51\% of medium and
% long-running projects do not use parallel features to run test
% suites.}\Mar{please make it consistent with research
% question}\Mar{explain this is over(under)-estimated...}

\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}ccc}
        \toprule
        \multirow{2}{*}{Group} %1st row, 1st cell
            & \multirow{2}{*}{\# \pomf{}}
	    & \# \pomf{} matched\\
        % 2nd row - empty cell
            & % empty cell
            & / total\\%
        \midrule%
	Long   & \numPomLong{} & 4 / \numLong{}\\%
	Medium & \numPomMed{} & 6 / \numMed{}\\%
        \midrule%
        Total % last row, first cell
            & \pomMedLong{}
            & \numProjectsPar{} / \numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallelization settings in build files: the
    first column indicates the group of projects according to their
    time cost; the second column is the subset of files with parallelization
    keywords; the last column indicates the ratio of projects with
    parallelism support.}
    \label{tab:inspection-table} 
\end{figure}

\Jbc{rework this... $\rightarrow$} From the \numProjectsPar{} projects
identified above, we investigated further the \numPomMatched{}
build files with parallel settings.  We analyzed the support and
distribution of parallel modes from this subset of projects. To
calculate the distribution of parallel modes, we considered only the
presence of the mode in at least one of the project settings.  Recall
that a build file may contain more than one parallel setting and a
project may contain several sub-modules with build files.  In case the
value of a parallel option is resolved dynamically (\eg, via
command-line argument or system variable) we compute all modes related
to the option. For instance, depending on the value, the
\CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes-static} summarizes our findings.
\Fix{Missing conclusion: Fork the most used configuration}

@@
